---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tinytiger

<!-- badges: start -->
<!-- badges: end -->

The goal of `tinytiger` is to provide a lightweight interface to the US Census Bureau's TIGER/Line Shapefiles.

## Installation

You can install the development version of `tinytiger` like so:

``` r
remotes::install_github('alarm-redist/tinytiger)
```

## Example

`tinytiger` provides lightweight functions to download Census Bureau TIGER/Line Shapefiles.

```{r example}
library(tinytiger)
## basic example code
```

To download a geography, simply use the function corresponding to one of the supported geographies.
```{r}
tt_counties('NY')
```


## Supported Geographies:
## Progress
- `tt_address_ranges()`: Address Ranges
- `tt_ai_an_nh_areas()`: American Indian / Alaska Native / Native Hawaiian Areas
- `tt_tribal_subdivisions()`: Tribal Subdivisions
- `tt_anrc()`: Alaskan Native Regional Corporations
- `tt_area_landmarks()`: Area Landmarks
- `tt_area_water():` Area Water
- `tt_block_groups()`: Block Groups
- `tt_cbsa()`: Core Based Statistical Areas
- `tt_congressional_districts()`: Congressional Districts
- `tt_new_england_combined_areas()`: Combined New England Towns and Cities
- `tt_coastline()`: Coastline
- `tt_consolidated_cities`: Consolidated Cities
- `tt_county()`: Counties
- `tt_county_subdivision()`: County Subdivisions
- `tt_csa()`: Combined Statistical Areas
- `tt_polygon_edges()`: All Polygon Edges
- `tt_elementary_school_districts()`: Elementary School Districts (limited states)
- `tt_estates()`: Estates (Virgin Islands only)
- `tt_polygon_faces()`: All Polygon Faces
- `tt_linear_water():` Linear Water
- `tt_metropolitan_divisions()`: Metropolitan Divisions
- `tt_military()`: Military Installations
- `tt_new_england_cities()`: New England Cities and Towns
- `tt_new_england_city_divisions()`: New England Cities and Towns Divisions
- `tt_places()`: Census Places
- `tt_point_landmarks()`: Point Landmarks
- `tt_primary_roads()`: Primary Roads
- `tt_primary_secondary_roads()`: Primary and Secondary Roads
- `tt_puma()`: Public Use Microdata Areas
- `tt_rails()`: Railroads
- `tt_roads()`: Roads
- `tt_secondary_school_districts()`: Secondary School Districts (limited states)
- `tt_state_leg_lower()`: Lower State Legislative Districts
- `tt_state_leg_upper()`: Upper State Legislative Districts
- `tt_states()`: States
- `tt_subbarios()`: Subbarios (Puerto Rico only)
- `tt_blocks()`: Blocks
- `tt_tribal_block_groups()`: Tribal Block Groups
- `tt_tracts()`: Tracts
- `tt_tribal_tracts()`: Tribal Tracts
- `tt_uac()`: : Urban Areas
- `tt_unified_school_districts()`: Unified School Districts
- `tt_zcta()`: Zip Code Tabulation Areas
