---
title: "Using `tinytiger`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using tinytiger}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`tinytiger` is designed to be low dependency to allow packages and newer R users to use TIGER lines and shapefiles without accruing non-standard dependencies. It has four dependencies:
- `sf`, needed to work with shapefiles
- `curl`, needed for downloading the files from the Census Bureau
- `cli`, used to create clear errors, warnings, and messages.
- `glue`, used for constructing complex URLs and already a dependency of `cli`

While `cli` is not necessary, it fits within our goals that `tinytiger` to be friendly for package development and new users, as `cli` is one of the most-widely downloaded R packages and comes with but one dependency itself.


## Using `tinytiger`

```{r setup}
library(tinytiger)
```

`tinytiger` has methods to download TIGER shapes for most Census geographies.
A full list are available on the [`tinytiger` website](https://alarm-redist.org/tinytiger/index.html#supported-geographies).

To download any shapes, we can use the corresponding function for the geography. 
All functions are prefixed with `tt_`.

For counties, for example, we can run:

```{r, eval = FALSE}
counties <- tt_counties()
```

```{r, echo = FALSE}
# depends on (1) internet and (2) successful download
counties <- NULL
try(counties <- tt_counties())
dl_success <- !is.null(counties)
```

```{r, eval = dl_success}
head(counties)
```


Other options for downloads are:

`r paste0("* \x60", setdiff(ls("package:tinytiger"), c("county_fips_2020", "tt_cache_clear", "tt_cache_path", "tt_cache_size")), "()\x60", collapse="\n")`
